Benchmarks

### 2012-10-19 docs/roadmap/benchmarks.tex
Nits.

% --------------------------------------------------------------------------------
\subsection*{Graphic cards}
\def\unt#1{& \footnotesize #1}
\begin{center}\begin{tabular}{lrrr} \toprule
\bf Paper		&				& \bf -- 		& \bf  ATLP\cite{gpu_atlp} \\ \midrule
Serie		&				& GeForce	& Tesla \\
Model		&				& GT 650M	& C1060 \\
Architecture	&				& Kepler		& GT200 \\
Capability		&				& 3.0		& 1.3 \\
Memory \unt{Mb}				& 1024		& 4096 \\
CUDA cores &					& 384		& 240 \\
Core clock \unt{MHz}			& 756		& 1300 \\
Memory clock \unt{MHz}			& 1953		& 1600 \\
Memory bus \unt{bit}				& 128		& 512 \\
Memory bandwidth \unt{GB/s}		& 28.8		& 102.4 \\
Processing power \unt{GFLOPS}	&564.5		& 622.08 \\ \midrule
\bf Processing speedup & 		& 1			& 1.07 \\
\bf Memory speedup & 			& 1			& 3.55 \\ \bottomrule
\end{tabular}\end{center}

@@

% --------------------------------------------------------------------------------
\subsubsection*{Preliminary results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(ms) & \bf T(ms) & \bf P(ms) \\ \midrule
1024 & 32 & CPU baseline & 1965.63 & 1191.13 & 6069.66 \\
1024 & 32 & GPU baseline & 838.67 & 499.87 & 516.82 \\
1024 & 32 & GPU sync improved & 642.37 & 316.40 & 343.29 \\

>>>>

% --------------------------------------------------------------------------------
\subsection*{Graphic cards\footnote{Source: \url{http://en.wikipedia.org/wiki/Comparison_of_Nvidia_graphics_processing_units}}}
\def\unt#1{& \footnotesize #1}
\begin{center}\begin{tabular}{lrrrr} \toprule
\bf Paper		&				& \bf -- 		& \bf  ATLP\cite{gpu_atlp} & \bf SWMB\cite{swat_mega} \\ \midrule
Serie		&				& GeForce	& Tesla	& GeForce  \\
Model		&				& GT 650M	& C1060	& GTX 560 \\
Architecture	&				& Kepler		& GT200	& GF114 \\
Capability		&				& 3.0		& 1.3	& 2.1 \\
Memory \unt{Mb}				& 1024		& 4096	& 1024 \\
CUDA cores &					& 384		& 240	& 384 \\
Core clock \unt{MHz}			& 756		& 1300	& 822 \\
Memory clock \unt{MHz}			& 1953		& 1600	& 4008 \\
Memory bus \unt{bit}				& 128		& 512	& 256 \\
Memory bandwidth \unt{GB/s}		& 28.8		& 102.4	& 128.26 \\
Processing power \unt{GFLOPS}	&564.5		& 622.08	& 1263.4 \\ \midrule
\bf Processing speedup & 		& 1			& 1.07	& \\
\bf Memory speedup & 			& 1			& 3.55	& \\ \bottomrule
\end{tabular}\end{center}

@@

\subsubsection*{SWMB\cite{swat_mega}}
\begin{center}\begin{tabular}{rlrr} \toprule
\bf Matrix size & \bf Sequences & \bf No pruning & \bf Pruning \\ \midrule
162K $\times$ 172K		& NC\_000898.1, NC\_007605.1	& 1.2 & 1.2 \\
543K $\times$ 536K		& NC\_003064.2, NC\_000914.1	& 10.8 & 10.8 \\
1044K $\times$ 1073K	& CP000051.1, AE002160.2		& 40.3 & 36.2 \\
3147K $\times$ 3283K	& BA000035.2, BX927147.1		& 363.6 & 363.2 \\ 
5227K $\times$ 5229K	& AE016879.1, AE017225.1		& 962.4 & 469.5 \\
7146K $\times$ 5227K	& NC\_005027.1, NC\_003997.3	& 1309 & 1309 \\
23012K $\times$ 24544K	& NT\_033779.4, NT\_037436.3	& 19701 & 19694 \\
59374K $\times$ 23953K	& NC\_000024.9, NC\_006492.2	& 49634 & 46869 \\
32799K $\times$ 46944K	& BA000046.3, NC\_000021.7		& 53869 & 29133 \\ \bottomrule
\end{tabular} \\[4pt] Smith-Waterman, timing in seconds \end{center}

% --------------------------------------------------------------------------------
\subsubsection*{Intermediate results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(ms) & \bf T(ms) & \bf P(ms) \\ \midrule
1024 & 32 & CPU baseline & 1965.63 & 1191.13 & 6069.66 \\
1024 & 32 & GPU baseline & 838.67 & 499.87 & 516.82 \\
1024 & 32 & GPU sync improved & 642.37 & 316.40 & 343.29 \\
